SNEAP2021 Figures

### 2021-04-30 doc/SNEAP2021/SNEAP2021_figures.Rmd
Redo secondaries figure. convert plots to svg

```{r, message = FALSE}
df <- map_dfr(list.files(here("data_analysed"), full.names = TRUE), read_csv) %>% 
  mutate(fm_normdiff = normFm(mean, fm_consensus),
         fm_sigma = sigma(mean, fm_consensus, merr),
         fmbc_normdiff = normFm(fm_lbc, fm_consensus),
         fmbc_sigma = sigma(fm_lbc, fm_consensus, merr))
```

@@

```{r}
df %>% 
  filter(fm_normdiff < 1) %>% 
ggplot(aes(fm_consensus, fm_normdiff)) +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = fm_normdiff - merr, ymax = fm_normdiff + merr)) +
  geom_point() +
  ggtitle("Difference in measured Fm vs. consensus")
```
```{r}
ggplot(df, aes(fm_consensus, diff)) +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = diff - merr, ymax = diff + merr)) +
  geom_point() +
  ggtitle("Difference in LBC-corrected vs consensus")
```

@@

>>>>

```{r, message = FALSE}
df <- map_dfr(list.files(here("data_analysed"), full.names = TRUE), read_csv) %>% 
  filter(!is.na(rec_num)) %>% 
  mutate(fm_diff = mean - fm_consensus,
         fm_normdiff = normFm(mean, fm_consensus),
         fm_sigma = sigma(mean, fm_consensus, merr),
         fmbc_diff = fm_lbc - fm_consensus,
         fmbc_normdiff = normFm(fm_lbc, fm_consensus),
         fmbc_sigma = sigma(fm_lbc, fm_consensus, merr))
```

@@

```{r}
df %>% 
  filter(fm_normdiff < 1) %>% 
ggplot(aes(fm_consensus, fm_normdiff)) +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = fm_normdiff - merr, ymax = fm_normdiff + merr)) +
  geom_point() +
  ggtitle("Difference in measured Fm vs. consensus")
```

@@

### difference from consensus

```{r}
secs <- df %>% 
  filter(fm_diff < .1) %>% 
ggplot(aes(fm_consensus, fm_diff, color = Cur)) +
  geom_hline(yintercept = 0) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_pointrange(aes(ymin = fm_diff - merr, ymax = fm_diff + merr)) +
  geom_point() +
  lims(x = c(0, 1.1),
       y = c(-.15, .15)) +
  ggtitle("Difference from consensus",
          subtitle = "Uncorrected") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank())
```

```{r}
secs_lbc <- df %>% 
  filter(fm_diff < .1) %>% 
  mutate(mean_diff = mean(fmbc_diff)) %>% 
ggplot(aes(fm_consensus, fmbc_diff, color = Cur)) +
  geom_hline(yintercept = 0) +
  geom_smooth(method = "lm", se = FALSE) +
  #geom_hline(yintercept = mean_diff) +
  geom_pointrange(aes(ymin = fmbc_diff - merr, ymax = fmbc_diff + merr)) +
  geom_point() +
  lims(x = c(0, 1.1),
       y = c(-.15, .15)) +
  labs(subtitle = "LBC-corrected")
```

```{r}
secs / secs_lbc
```
